---
title: "Aggregating Anteaters Project"
author: "B155926, B239086, B239979, B244840, and B246814"
output: bookdown::html_document2
---
<style>
    h1 {font-size: 1.8em;}
    h2 {font-size: 1.6em;}
    h3 {font-size: 1.4em;}
    title {font-size: 2.2em;}
</style>

```{r setup, include=FALSE}
# Formatting ----
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
options(scipen=999)


# Load required libraries ----
library(bookdown)
library(car)
library(tinytex)
library(tidyverse)
library(GGally)
library(ggExtra)
library(sjPlot)
library(kableExtra)
library(patchwork)
library(MKinfer)
library(RColorBrewer)

set.seed(010298)

# Download data ----
source("https://edin.ac/4616rYu")
get_my_data(group_name = "aggregating_anteaters")

# functions ----
print_p <- function(p) {
  print <- ifelse(p < 0.001, "< 0.001", str_c("= ", round(p,3)))
  return(print)
}

l2p <- function(logits) {
  odds <- exp(logits)
  prob <- odds/(1 + odds)
  return(prob)
}
```

# Data Preparation

```{r data cleaning}
# cleaning data ----
emoji_clean <- emoji |>
  filter(is.na(age) == F,
         age > 2,
         em_cat != "upside-down face",
         freq_emu >= 0) |>
  mutate(opsys = ifelse(opsys == "appple", "apple", opsys),
         opsys = factor(opsys, labels = sapply(unique(opsys), str_to_sentence)),
         em_cat_emoji = sapply(em_cat, emoji::emoji),
         em_cat = factor(em_cat,labels = sapply(unique(em_cat), str_to_sentence)),
         EI = factor(EI, labels = sapply(unique(EI), str_to_sentence)))

# exlcuded data table ----
excl_tab <- emoji |> 
  mutate(
    exclusion_reason = ifelse(is.na(name) == T, 
                              "Name is missing",
                        ifelse(is.na(age) == T, 
                               "Age is missing",
                        ifelse(age < 7,
                               "Impossible or unlikely age",
                        ifelse(is.na(opsys) == T,
                               "Operating system is missing",
                        ifelse(is.na(freq_emu) == T,
                               "Frequency of Emoji use is missing",
                        ifelse(freq_emu < 0,
                               "Impossible frequency value (negative) is reported",
                        ifelse(is.na(em_cat) == T,
                               "Emoji category is missing",
                        ifelse(em_cat != "loudly crying face" &
                                 em_cat != "slightly smiling face" &
                                 em_cat != "thumbs up",
                               "Emoji not in study materials is reported",
                        ifelse(is.na(EVS) == T,
                               "Emotional valence score is missing",
                        ifelse(is.na(EI) == T,
                               "Emoji Interpretation is missing",
                               "not excluded"))))))))))) |>
  filter(exclusion_reason != "not excluded")
```

Before starting to describe and analyse the data, we checked that all observations were entered within the possible range of each continuous variable and levels of categorical variables. We inspected visualisations of the marginal distributions of and relationships amongst the variables to identify observations with impossible values (see Figure \@ref(fig:ini-pairs-panels) in the Appendix). We excluded all impossible values (e.g., a negative reported frequency of emoji use) along with any observations containing missing data (N~excluded~ = `r nrow(excl_tab)`). Table \@ref(tab:exclude) in the Appendix provides an overview of excluded data points and the reason for exclusion. Finally, we corrected 'Appple' to 'Apple' for operating system of `r nrow(filter(emoji, opsys=="appple"))` observations.

# Data Description and Initial Tests

## Difference Between Operating System and Frequency of Emoji Use

First, we investigated if there is a difference in how frequently emojis were used between users of Apple and Android operating systems. Figure \@ref(fig:q1b-violin-plot), shows that the lower quartile and median of the two operating systems were similar. However,  the upper quartile is higher and the overall range is larger for Apple than Android. It seems that Apple users are more likely to use a higher number of emojis per day. There are only three  unusually high values all reported by Apple users.

```{r q1b-violin-plot, fig.cap="Frequency of Emoji Use on Apple and Android Operating System", fig.align='center', fig.height = 3}
emoji_clean |>
  filter(opsys !="Windows") |>
ggplot(aes(x = opsys, y = freq_emu, fill = opsys)) + 
  geom_jitter(alpha = .3, height = 0)+
  geom_violin(alpha = 0.5) +
  geom_boxplot(width=0.1) + 
  scale_fill_brewer(palette = "Accent")+
  labs(x = "Operating system", y = "Frequency of emoji use (emoji/day)", fill="Operating System")+
  theme_light()
```

```{r}
# t-test ----
q1t_test <-t.test(freq_emu ~ opsys, data = filter(emoji_clean, opsys != "Windows"))

# shapiro Wilks + equal variance test ----
emoji_qq2 <- emoji_clean|>
  filter(opsys=="Android")
shappy_wilks_and <- shapiro.test(emoji_qq2$freq_emu) # greater than 0.05
emoji_qq1 <- emoji_clean|>
  filter(opsys=="Apple")
shappy_wilks_app <- shapiro.test(emoji_qq1$freq_emu) # greater than 0.05
var_test <- var.test(freq_emu ~ opsys, filter(emoji_clean, opsys != "Windows"))

# bootstrap standard error
boot_t_test <- boot.t.test(freq_emu ~ opsys, alternative = "two.sided", R = 1000, conf.level =0.95, var.equal = T, data = filter(emoji_clean, opsys != "Windows"))
```

Initially, we conducted a two-tailed Welch two sample t-test ($\alpha$ = 0.05) to assess whether the mean frequency of emoji use was different between Android (*Android n* = `r nrow(filter(emoji_clean, opsys == "Android"))` ; *m* = `r round(q1t_test$estimate [1],1)`; *sd* = `r round(sd(filter(emoji_clean, opsys == "Android")$freq_emu), 2)`) and Apple users (*n* = `r nrow(filter(emoji_clean, opsys == "Apple"))`; *m* = `r round(q1t_test$estimate[2],2)`; *sd* = `r round(sd(filter(emoji_clean, opsys == "Apple")$freq_emu), 2)`) while accounting for the unequal variances in the two groups (see sds; supported by F test of the variance ratio; *F*(`r var_test$parameter[1]`, `r var_test$parameter[2]`) = `r round(var_test$statistic,2)`, *p* `r print_p(var_test$p.value)`). This indicated a significantly higer mean emoji use frequency used Apple users compared to Android users, *t*(`r round(q1t_test$parameter,2)`) = `r round(q1t_test$statistic,2 )`, *p* `r print_p(q1t_test$p.value)`, two-tailed). However, this test assumes normally distributed values of frequency of emoji use in each group, which was not the case as shown by Q-Q plots (see appendix, Figure \@ref(fig:qq-plot-freq)) and corroborated by Shapiro-Wilks tests indicating significantly non-normal distributions (Android: *W* = `r round(shappy_wilks_and$statistic)`, *p* = `r print_p(shappy_wilks_and$p.value)`; Apple: *W* = `r round(shappy_wilks_app$statistic)`,  *p* = `r print_p(shappy_wilks_app$p.value)`). This may affect the estimation of the standard error and, in turn, the reported significance. Given the large sample size (n > 200), we conducted a sensitivity analysis using bootstrapped 95 % confidence intervals, as this way of estimating standard error has no assumptions about normality. The bootstrapped estimated mean frequency of emoji use was `r  abs(round(boot_t_test$boot.estimate,2))` lower in Android users compared to Apple users (95 % *CI*[`r round(boot_t_test$boot.conf.int[1], 2)`, `r round(boot_t_test$boot.conf.int[2],2)`]. The non-zero containing confidence interval of this mean difference supports the conclusion from the Welch t-test without the assumption of normal group populations that Apple users indeed used emojis more frequently than Android users.

## Correlation Between Age and Frequency of Emoji Use

```{r}
shappy_wilks <- shapiro.test(emoji_clean$freq_emu) # greater than 0.05
shappy_wilks2 <- shapiro.test(emoji_clean$age) # greater than 0.05
```

To assess if there is a relationship between participant age (*m* = `r round(mean(emoji_clean$age),2 )`, *sd* = `r round(sd(emoji_clean$age),2 )`) and the frequency of their emoji use (*m* = `r round(mean(emoji_clean$freq_emu),2 )` (*sd* = `r round(sd(emoji_clean$freq_emu),2 )`), we planned to conduct a Pearson correlation test. However, upon visualising these variables and their relationship in Figure \@ref(fig:cor-plot), these do not conform to the assumptions of a Pearson correlation coefficient. Firstly, age and frequency seem to co-move in a negative but non-linear fashion. The accompanying histograms reveal that the frequency of emoji and age are not normally distributed, as verified by Shapiro–Wilk tests (Frequency of emoji use: *W* = `r round(shappy_wilks$statistic, 2)`, *p* `r print_p(shappy_wilks$p.value)`; Age: *W* = `r round(shappy_wilks2$statistic, 2)`, *p* `r print_p(shappy_wilks2$p.value)`) with the former seeming to follow a Poisson distribution while latter is largely uniform. Since normally distributed variables with a linear relationship are assumed for a Pearson correlation test, we conducted a Spearman's rank correlation test, which tests for a monotonic relationship between two variables without assumptions about the normality of their distributions or the linearity of their relationship. 

```{r cor-plot, fig.cap="Relationship Between Age and Frequency of Emoji Use", fig.align='center', fig.height = 3.3}
p_cor <- ggplot(emoji_clean, aes(x=age, y=freq_emu)) + 
  geom_point(alpha = 0.5) + 
  labs(x = "Age",
       y = "Frequency of emoji use (emoji/day)")+
  theme_light()
ggMarginal(p_cor, type = "hist", xparams = list(binwidth = 1, fill = "#CBD6E8"), yparams = list(binwidth = 1, fill = "#F4CAE3"))
```

```{r correlation test}
q1b_cortest_np <- cor.test(emoji_clean$age, emoji_clean$freq_emu, method= "spearman")
```

The Spearman's rank correlation test (`r nrow(emoji_clean)`) indicated that there was a significant strong negative correlation between age of an individual and the frequency of emoji use (*R* = `r round(q1b_cortest_np$estimate,2)`, *S* = `r round(q1b_cortest_np$statistic,2)`), *p* `r print_p(q1b_cortest_np$p.value)`). Thus, while not linearly, it seems like as age increased, emojis were used less frequently.

## Balance of Users of Operating Systems for Emoji Categories

Finally, we investigated whether there is a balance between Apple and Android users for each category of emoji. Figure \@ref(fig:q1c-bar-plot) shows the distribution of these operating systems for each emoji category. For all categories, the number of Apple users seem slightly larger than Android users, with the largest difference for the thumbs up emoji (`r emoji::emoji("thumbs up")`). We conducted a $\chi^2$ goodness of fit test for *each* emoji category to test if the observed proportion of participants using each operating system deviated from a hypothesised equal proportion of users (50% each), which would indicate balance.

```{r q1c-bar-plot, fig.cap="Distribution of Participants on Apple and Android Operating System for Each Emoji Category", fig.height = 2.3, fig.align='center'}
ggplot(data = filter(emoji_clean, opsys != "Windows"), aes(x = em_cat, fill = opsys))+
  geom_bar(position = "dodge", color = "black") +
  labs(fill = "Operating System Used", x = "Emoji Category", y = "Number of Participants")+
  scale_fill_brewer(palette = "Pastel2")+
  theme_light()
```

```{r chi square test}
# chi square tests ----
# chi square for loudly crying face
q1_chisq_cry <- emoji_clean |>
  filter((opsys == "Apple" | opsys == "Android") & em_cat == "Loudly crying face") |>
  droplevels() |>
  select(opsys) |>
  table() |>
  chisq.test()

# chi square for slightly smiling face
q1_chisq_smile <-emoji_clean |>
  filter((opsys == "Apple" | opsys == "Android") & em_cat == "Slightly smiling face") |>
  droplevels() |>
  select(opsys) |>
  table() |>
  chisq.test()

# chi square for thumbs up
q1_chisq_thumb <-emoji_clean |>
  filter((opsys == "Apple" | opsys == "Android") & em_cat == "Thumbs up") |>
  droplevels() |>
  select(opsys) |>
  table() |>
  chisq.test()

# proportion table ----
prop <- emoji_clean |>
  filter(opsys != "Windows") |>
  droplevels() |>
  group_by(em_cat,opsys)|>
  summarise(n = n()) |>
  mutate(total_n =sum(n[em_cat == em_cat]),
    prop = round(n/total_n*100,2)) 
```

For each emoji category, we found no significant difference between the observed proportions of Apple and Android users and equal proportions: for loudly crying face emoji (`r emoji::emoji("loudly crying face")`) (*n* = `r nrow(filter(emoji_clean, opsys != "Windows" & em_cat == "Loudly crying face"))`, *proportion~Apple~* = `r filter(prop, opsys == "Apple" & em_cat == "Loudly crying face")$prop` %; $\chi^2$ (`r q1_chisq_cry$parameter`) = `r round(q1_chisq_cry$statistic, 2)`, *p* `r print_p(q1_chisq_cry$p.value)`); for the slightly smiling face  emoji (`r emoji::emoji("slightly smiling face")`) (*n* = `r nrow(filter(emoji_clean, opsys != "Windows" & em_cat == "Slightly smiling face"))`, *proportion~Apple~* = `r filter(prop, opsys == "Apple" & em_cat == "Slightly smiling face")$prop` %; $\chi^2$ (`r q1_chisq_smile$parameter`) = `r round(q1_chisq_smile$statistic, 2)`, *p* `r print_p(q1_chisq_smile$p.value)`); and for the thumbs up emoji (`r emoji::emoji("thumbs up")`) (*n* = `r nrow(filter(emoji_clean, opsys != "Windows" & em_cat == "Thumbs up"))`, *proportion~Apple~* = `r filter(prop, opsys == "Apple" & em_cat == "Thumbs up")$prop` %, $\chi^2$ (`r q1_chisq_thumb$parameter`) = `r round(q1_chisq_thumb$statistic, 2)`, *p* `r print_p(q1_chisq_thumb$p.value)`). Thus, we found no evidence of imbalance of users of Apple and Android operated phones in any of the emoji categories.

# The Emotional Effect of Emoji

```{r}
# Original model ----
m2intq2 <- (lm(scale(EVS) ~ freq_emu + I(age-mean(age)) * em_cat , data = emoji_clean))
ano_q2 <- anova(m2intq2)

# Assumptions ----
shapiro_wilks_int <- shapiro.test(residuals(m2intq2)) #normality
ncvTest_int <- ncvTest(m2intq2)#(testing) constant variance #above the text - otherwise can't see them. 

# Sensitivity analyses ----
m2intq2_sensitivity <- (lm(scale(EVS) ~ freq_emu + I(age-mean(age)) * em_cat , data = emoji_clean[-c(2,13,175), ]))
ano_q2_sense <- anova(m2intq2_sensitivity)

shapiro_wilks_sensitivity <- shapiro.test(residuals(m2intq2_sensitivity))
ncvTest_sensitivity <- ncvTest(m2intq2_sensitivity)
```

The first research aim that we addressed were which factors influenced the emotional valence of emoji. We fitted a multiple regression model with frequency as the initial predictor due to its known effect on emotional valence score, the type of emoji, as well as participant age, and the interaction between age and emoji category to investigate the effect of age on emotional content of emoji and whether this differs between emojis. We mean-centered age (*m* = `r round(mean(emoji_clean$age),2)`) and scaled the emotional valence score by its standard deviation (*sd* = `r sd(emoji_clean$EVS)`) allowing us to interpret the intercept at the mean age and coefficients as change in terms of standard deviations of emotional valence score. Emoji category was treatment coded with the "loudly crying face" emoji (`r emoji::emoji("loudly crying face")`) as the reference level (see \@ref(tab:cat-code-tab)).

Figure \@ref(fig:q2-desc-plots) provides an overview of the predictors, emotional valence score, and their relationships. Emotional valence score was normally distributed (Figure \@ref(fig:q2-desc-plots)C). As noted previously, this was not the case for age(Figure \@ref(fig:q2-desc-plots)D) and frequency of Emoji use (Figure \@ref(fig:q2-desc-plots)E). There were slightly more participants who rated the loudly crying face emoji [`r emoji::emoji("loudly crying face")`] than the other emoji categories (Figure \@ref(fig:q2-desc-plots)). Figure \@ref(fig:q2-desc-plots)B also indicates a negative relationship between age and emotional valence score; as age increases, the emotional valence score decreases. This decrease seem more pronounced in the loudly crying face emoji group [`r emoji::emoji("loudly crying face")`] than the other categories.

```{r q2-desc-plots, fig.cap="Relationships (A-B) and Marginal Distributions (C-F) of Variables of Interest for Emotional Effect", fig.width=11, fig.height = 5.5}
# shut down----
p_age_evs <- ggplot(emoji_clean, aes(x = EVS, y = age, color = em_cat,
                                     fill = em_cat))+
  geom_smooth(method = "lm")+
  geom_jitter(alpha = .3, height = 0)+
  scale_color_brewer(palette = "Accent")+
  scale_fill_brewer(palette = "Accent")+
  facet_wrap(~em_cat)+
  labs(x = "Emotional valence score", y = "Age",
       title = "(B) Emotional Valence Score by Age for each Emoji Category")+ 
  theme_light()+
  theme(legend.position = "none",
        strip.background = element_rect(fill ="white", color = "grey"),
        strip.text = element_text(color = "black"),
        plot.title = element_text(size = 11))

p_freq_evs <- ggplot(emoji_clean, aes(x = EVS, y = freq_emu))+
  geom_smooth(method = "lm", color = "#386CB0", fill = "#386CB0")+
  geom_jitter(alpha = .3, height = 0, color = "#386CB0")+
  labs(x = "Emotional valence score", y = "Frequency of emoji use",
       title = "(A) Emotional Valence Score by Frequency of Emoji Use")+ 
  theme_light()+
  theme(legend.position = "none",
        strip.background = element_rect(fill ="white", color = "grey"),
        strip.text = element_text(color = "black"),
        plot.title = element_text(size = 11))

p_evs <- ggplot(emoji_clean, aes(x = EVS))+
  geom_density(color = "black", fill = "#8DD3C7") +
  labs(x = "Emotional valence score", y = "Density", title = "(C) Emotional Valence Score" )+
  theme_light()+
  theme(plot.title = element_text(size = 11))

p_em_cat <- ggplot(emoji_clean, aes(x = em_cat))+
  geom_bar(color = "black", fill = "#FB8072")+
  labs(x = "Emoji category", y = "Participant count", title = "(F) Emoji Category")+
  theme_light()+
  theme(plot.title = element_text(size = 11),
        axis.text.x = element_text(angle = 14))

p_age <- ggplot(emoji_clean, aes(x = age))+
  geom_density(color = "black", fill = "#CBD6E8") +
  labs(x = "Age", y = "Density", title = "(D) Age" )+
  theme_light()+
  theme(plot.title = element_text(size = 11))

p_freq <- ggplot(emoji_clean, aes(x = freq_emu))+
  geom_density(color = "black", fill = "#F4CAE3") +
  labs(x = "Frequency (emoji/day)", y = "Density", title = "(E) Frequency of Emoji Use") +
  theme_light()+
  theme(plot.title = element_text(size = 11))

(p_freq_evs| p_age_evs) / (p_evs|p_age|p_freq|p_em_cat) + plot_layout(heights = c(2,1))
```

We conducted the following tests ($\alpha$ = .05) to address which factors influenced emotional valence score and how. Firstly, we conducted an analysis of variance (ANOVA) to test which predictors significantly improved model fit by significantly reducing sum of squared residuals according to an *F*-test. Then we examined the specific influences of age and its interaction with emoji category via the regression coefficients given the researchers' interest in these. We evaluated these by their direction (i.e., how they influence emotional valence), estimate range (95 % confidence intervals), and significance with *t*-tests ($H_0: \hat\beta_i \neq 0$). Before performing these, we assessed if the fitted model complied with the assumptions of linear regression ($\varepsilon$ ~ $N(\frac{0}{var})$). Given the strong correlation between age and frequency of emoji use (see Correlation Between Age and Frequency of Emoji Use), we confirmed that multicollinarity, i.e., correlated predictors biasing model estimates, was negligible by estimating generalised variance inflation factors for each predictor (all below the a priori criterion of 5; see the Appendix Table \@ref(tab:q2-vif)). Heteroscedacity appeared unproblematic from a visual inspection the $\sqrt{standardised \ residuals}$ across fitted values (see Appendix, Figure \@ref(fig:ass-for-q2)C) although a Breusch-Pagan test indicated that residuals were significantly non-homoscestedastic ($\chi^2$ (`r (ncvTest_int$Df)`) = `r round(ncvTest_int$ChiSquare,2)`, *p* `r print_p(ncvTest_int$p)`). Likewise, a significant Shapiro-Wilks (*W* = `r round(shapiro_wilks_int$statistic,2)`, *p* `r print_p(shapiro_wilks_int$p.value)`) indicated non-normal residuals, however, these seemed normally distributed (see Appendix, Figure \@ref(fig:ass-for-q2)B) except three outliers. Upon inspecting Cook's distances, we identified and excluded three values exerting undue influence on model estimated coefficients (see Appendix, Figure \@ref(fig:ass-for-q2) and Table \@ref(tab:q2-influence); all above a priori threshold determined by $\frac{4}{N-k-1}$ = `r round(4/(237-3-1),2)`^[where *N* is the number of observations (`r nrow(emoji_clean)`) and *k* is the number of model predictors (4)]) as a sensitivity analysis (see Table \@ref(tab:tab-model)) found changes to coefficient significances upon their removal. The residuals of the model fitted to this reduced dataset also complied to the assumptions of normality (as the excluded observations were also outliers in the Q-Q plot; *W* = `r round(shapiro_wilks_sensitivity$statistic,2)`, *p* `r print_p(shapiro_wilks_sensitivity$p.value)`) and homoscedasticity ($\chi^2$ (`r (ncvTest_sensitivity$Df)`) = `r round(ncvTest_sensitivity$ChiSquare,2)`, *p* `r print_p(ncvTest_sensitivity$p)` ).

```{r q2-ano}
ano_row <- c( 
  "Emoji usage", 
  "Age",
  "Emoji category",
  "Age:Emoji category",
  "Residuals")

rownames(ano_q2_sense) <- ano_row
  
ano_q2_sense |>
  rename("p.value" = "Pr(>F)") |>
  rename("f.value" = "F value") |>
  mutate(Df = ifelse(is.na(Df) == T, "", Df),
         f.value = ifelse(is.na(f.value) == T, "", round(f.value,2)),
         p.value = ifelse(is.na(p.value) == T, "", ifelse(p.value < 0.001, "< 0.001", round(p.value,3)))) |>
  kable(digits = 2, 
        # proper column names
        col.names = c("Df", 
                      "Sum of Squares", 
                      "Mean Sum of Squares", 
                      "F value", 
                      "P value"),
        caption = "Emotional Effect of Emojis: Analysis of Variance Table (Sensitivity Analysis)",
        booktabs = T) |> 
  kable_styling(htmltable_class = "lightable-classic", position = "float_right", full_width = T)
```

```{r tab-model}
tab_model(m2intq2, m2intq2_sensitivity,show.stat=T, 
          dv.labels = c("Emotional Valence (Full Dataset Model)", "Emotional Valence (Reduced Dataset Model"), 
          pred.labels = c("Intercept", 
                          "Emoji use frequency", 
                          "Age", 
                          str_c("Emoji [", emoji::emoji("slightly smiling face"),"]"), 
                          str_c("Emoji [", emoji::emoji("thumbs up"),"]"), 
                          str_c("Age:Emoji [", emoji::emoji("slightly smiling face"),"]"), 
                          str_c("Age:Emoji [", emoji::emoji("thumbs up"),"]")), 
          string.stat = "t-statistic ", 
          string.p = "p-value ", 
          string.ci = "95 % CI",
          show.r2 = T,
          show.se = T,
          title = "(\\#tab:tab-model) Emotional Effect of Emojis Model")
```

The model fitted to the reduced dataset accounted 46 % of the variance in the observed data (adjusted $R^2$ = `r round(summary(m2intq2_sensitivity)$r.squared,2)`). The ANOVA (in Table \@ref(tab:q2-ano)) indicated that only frequency of emoji use (*F*(`r ano_q2_sense$Df[1]`,`r  ano_q2_sense$Df[5]`) = `r round(ano_q2_sense$'F value'[1],2)`, *p* `r print_p(ano_q2_sense$'Pr(>F)'[1])`) and the interaction between age and emoji category (*F*(`r ano_q2_sense$Df[4]`,`r  ano_q2_sense$Df[5]`) = `r round(ano_q2_sense$'F value'[4],2)`, *p* `r print_p(ano_q2_sense$'Pr(>F)'[4])`) were found to significantly improve variance explained. Age, thus, did not significantly contribute to explaining variance in emotional valence scores above and beyond frequency of emoji use (*F*(`r ano_q2_sense$Df[2]`,`r  ano_q2_sense$Df[5]`) = `r round(ano_q2_sense$'F value'[2],2)`, *p* `r print_p(ano_q2_sense$'Pr(>F)'[2])`).

The models fitted to the full and reduced datasets are presented in Table \@ref(tab:tab-model). When excluding influential observations, both interaction terms between age and emoji category were significant indicating differences in the effect of age between all three emojis tested (with the full dataset the slightly smiling face emoji (`r emoji::emoji("slightly smiling face")`) was not different from the loudly crying face emoji for the effect of age; see Table \@ref(tab:tab-model)). For the loudly crying face emoji (`r emoji::emoji("loudly crying face")`), emotional valence was predicted to decrease by `r abs(round(m2intq2_sensitivity$coef[3],2))` sds (95 % *CI*[`r round(confint(m2intq2_sensitivity)[3,1],2)`, `r round(confint(m2intq2_sensitivity)[3,2],2)`]) for each year older the participant was (*t* = `r round(coef(summary(m2intq2_sensitivity))[,"t value"][3],2)`, *p* `r print_p(coef(summary(m2intq2_sensitivity))[,"Pr(>|t|)"][3])`). While for the slightly smiling face emoji (`r emoji::emoji("slightly smiling face")`) and the thumbs up emoji (`r emoji::emoji("thumbs up")`), age had a significantly smaller influence on the emotional valence score, increasing it relative to the age effect for the loudly crying face emoji (`r emoji::emoji("loudly crying face")`) by `r round(m2intq2_sensitivity$coef[6],2)` sds (95 % *CI*[`r round(confint(m2intq2_sensitivity)[6,1],2)`, `r round(confint(m2intq2_sensitivity)[6,2],2)`]; *t* = `r round(coef(summary(m2intq2_sensitivity))[,"t value"][6],2)`, *p* = `r print_p(coef(summary(m2intq2_sensitivity))[,"Pr(>|t|)"][6])`) and `r round(m2intq2_sensitivity$coef[7],2)` sds (95 % *CI*[`r round(confint(m2intq2_sensitivity)[7,1],2)`, `r round(confint(m2intq2_sensitivity)[7,2],2)`]; *t* = `r round(coef(summary(m2intq2_sensitivity))[,"t value"][7],2)`, *p* = `r print_p(coef(summary(m2intq2_sensitivity))[,"Pr(>|t|)"][7])`) respectively. These interactions are plotted in Figure \@ref(fig:q2-interaction-plot).

```{r q2-interaction-plot, fig.cap="The interaction of Age and Emoji Category on the EVS", fig.height=2.5, fig.width=9, fig.align='center'}
# plot interactions 
p2 <- interactions::interact_plot(m2intq2_sensitivity, pred = "age", modx = "em_cat", interval = TRUE, x.label = "Age", y.label = "Emotional Valence Score", legend.main = "Emoji Category")
p2
```

## Conclusion
We investigated how emotional valence is affected by the age of participants after accounting for frequency of emoji use and whether this differed for different emojis. We found that for the loudly crying face emoji (`r emoji::emoji("loudly crying face")`), age negatively affected its emotional valence. We found nearly no change in the emotional valence of the other emoji categories. Thus, age affected emotional valence negatively only for some emoji.

# Accuracy of Emoji Interpretation

```{r logistic regression and anova}
# data prep ----
emoji_q3_analysis <- emoji_clean |>
  mutate(EI_bi = ifelse(EI == "Incorrect", 0, 1),
         age_mc = I(age-mean(age)))

# model fit and analysis of deviance----
# model fit
m1q3 <- glm(EI_bi ~ freq_emu + age_mc*em_cat, data = emoji_q3_analysis, family = binomial)

m1q3_tests <-summary(m1q3)

# analysis of deviance
ano_q3 <- anova(m1q3, test = "Chisq") |>
  rename("p.value" = "Pr(>Chi)")

# Model coefficient plot ----

# Age for each emoji category while keeping frequency constant
q3_plotdata_age_em <- tibble(
  freq_emu = rep(0, 45*3),
  age_mc = rep(seq(min(emoji_q3_analysis$age_mc), max(emoji_q3_analysis$age_mc), 1),3),
  em_cat = c(rep(unique(emoji_clean$em_cat) [1], 45), 
             rep(unique(emoji_clean$em_cat) [2], 45),
             rep(unique(emoji_clean$em_cat) [3], 45))
)

# Age and emoji category plot
q3_p2 <- broom::augment(m1q3, newdata = q3_plotdata_age_em, 
               type.predict = "link",
               se_fit=TRUE) |>
  mutate(
    .lower = l2p(.fitted - 1.96*.se.fit),
    .upper = l2p(.fitted + 1.96*.se.fit),
    .fitted = l2p(.fitted),
    age = I(age_mc + mean(emoji_clean$age))
  ) |> 
  ggplot(aes(x=age,y=.fitted, group = em_cat, ymin=.lower,
             ymax=.upper))+
  geom_line(aes(color = em_cat))+
  geom_ribbon(alpha=.2, aes(fill = em_cat))+
  scale_colour_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  labs(x = "Age", y = "P(Correct Emoji Interpretation)", 
       color =  "Emoji Category", fill ="Emoji Category")+
  theme_light() +
  theme(legend.key = element_rect("white"),
        legend.background = element_rect(fill= "white", color ="black"),
        legend.position = c(0.7,0.8))
```

Finally, we address what factors make participants more or less likely to correctly interpret emojis (according to the researchers' coding scheme). The predictors of interest were the same as before; frequency of emoji use first to control for its known effect on interpreting emoji, and age and emoji category along with the interaction between these to investigate if there is an effect of age on interpretation accuracy and if this depends on the emoji. Figure \@ref(fig:q3-desc-plots) provides an overview of the marginal distribution of emoji interpretation accuracy (Figure \@ref(fig:q3-desc-plots)C; see Figure \@ref(fig:q2-desc-plots) for marginal distributions of predictors) and its relationships with age by emoji category (Figure \@ref(fig:q3-desc-plots)A) and for frequency of emoji use (Figure \@ref(fig:q3-desc-plots)B). Generally, a slightly higher proportion of participants interpreted their emoji incorrectly - the thumbs up emoji (`r emoji::emoji("thumbs up")`) seemed particularly hard to get correct while the louddly crying face emoji (`r emoji::emoji("loudly crying face")`) seemed to have a slightly higher proportion of correct responses (Figure \@ref(fig:q3-desc-plots)C). Examining the median age and frequency in Figures \@ref(fig:q3-desc-plots)A-B, it seems that incorrect responses are more common for older participants and for those who use emoji less frequently. Figure \@ref(fig:q3-desc-plots)A provided some indication that the emoji being interpreted may moderate the relationship between lower age and correct interpretations - specifically, that the thumbs up emoji (`r emoji::emoji("thumbs up")`) seem to have slightly lower median age for correct interpretations.

```{r q3-desc-plots, fig.cap="Relationships with Variables of Interest (A-B) and Marginal Distribution (C) for Interpretation Accuracy", fig.width=10, fig.height=4.5}
p_age_acc <- ggplot(emoji_clean, aes(x = EI, y = age, fill = em_cat))+
  geom_jitter(alpha = .3, height = 0)+
  geom_violin(alpha = 0.5) +
  geom_boxplot(width = 0.2) + 
  facet_wrap(~em_cat)+
  scale_fill_brewer(palette = "Accent")+
  labs(x = "Interpretation accuracy", y = "Age",
       title = "(A) Emoji Interpretation Accuracy for Age and Emoji Category")+ 
  theme_light()+
  theme(legend.position = "none",
        strip.background = element_rect(fill ="white", color = "grey"),
        strip.text = element_text(color = "black"),
        plot.title = element_text(size = 11))

p_freq_acc <- ggplot(emoji_clean, aes(x = EI, y = freq_emu, fill = EI))+
  geom_jitter(alpha = .3, height = 0)+
  geom_violin(alpha = 0.5) +
  geom_boxplot(width = 0.2) + 
  scale_fill_brewer(palette = "Set3")+
  labs(x = "Interpretation accuracy", y = "Frequency (emoji/day)", 
       title = "(B) Emoji Interpretation Accuracy Frequency of Emoji Use")+
  theme_light()+
  theme(legend.position = "none",
        plot.title = element_text(size = 11))

p_EI <- ggplot(emoji_clean, aes(x = EI, fill = em_cat))+
  geom_bar(color = "black")+
  scale_fill_manual(values = c("#C6DBEF" ,"#6BAED6", "#2171B5"))+
  ylim(c(0,230))+
  labs(x = "Interpretation accuracy", y = "Number of participants", 
       title = "(C) Emoji Interpretation Accuracy", fill = "Emoji category")+
  theme_light()+
  theme(legend.title = element_text(size = 10),
        legend.text = element_text(size=9),
        legend.key = element_rect("white"),
        legend.background = element_rect(fill= "white", color ="black"),
        plot.title = element_text(size = 11))

(p_age_acc | (p_freq_acc/p_EI) ) + plot_layout(widths = c(1.5,1))
```

Given the binary outcome (correct vs. incorrect interpretation; see Figure \@ref(fig:q3-desc-plots)C), we fitted a multiple logistic regression model via maximum likelihood estimation. This estimates the change in log odds ratio of correct interpretation for changes in each predictor (see eq. \@ref(eq:q3-model)). We included the predictors as outlined above. Like the previous model, we mean-centered age so that the log odds of the intercept were estimated for the mean age of the sample rather than extrapolated to age 0. We treatment coded emoji category with the loudly crying face emoji (`r emoji::emoji("loudly crying face")`) as the reference level  (coding scheme in the Appendix, Table \@ref(tab:cat-code-tab)). This provides two dummy coded variables ($D_1$ and $D2$ in eq. \@ref(eq:q3-model)) representing the mean difference in log odds of successful interpretation between this reference level and each of the slightly smiling face emoji (`r emoji::emoji("slightly smiling face")`) and the thumbs up emoji (`r emoji::emoji("thumbs up")`). Thus, we fitted a model where the intercept was the log odds ratio of correctly interpreting a loudly crying face emoji (`r emoji::emoji("loudly crying face")`) for a mean-aged participant reporting using 0 emoji/day. Equation \@ref(eq:q3-model) shows the exact model fitted:

\begin{align}
\log[ \frac {P(Correct)}{P(Incorrect)}] = & \ \hat\beta_0 + \hat\beta_{1}(Frequency) + \hat\beta_{2}(Age) + \hat\beta_{3}D_{1[slightly \ smiling \ face]} + \hat\beta_{4}D_{2[thumbs \ up]} \ + \\ 
& \ \hat\beta_{5}(Age · D_{1[slightly \ smiling \ face]}) + \hat\beta_{6}(Age · D_{2[thumbs \ up]}) (\#eq:q3-model)
\end{align} 

We conducted the following tests (all at $\alpha$ = .05 unless otherwise stated) to address which factors are associated with more or less likelihood of correctly interpreting the tested Emoji. Firstly, we tested if each of the predictors and the interaction significantly improved model fit with an analysis of deviance for the full model using likelihood ratio ($\chi^2$) tests to test if each significantly reduced model deviance. Secondly, we examined regression coefficients of age and its interaction, their direction, range with 95 % confidence intervals, and significance with *z*-tests ($H_0: \hat\beta_i \neq 0$). Before examining the model, we verified that the model fit did not violate assumptions of logistic regression by inspecting the range of the standardised deviance residuals (plotted in Figure \@ref(fig:q3-ass-diag)A; a priori criterion range: $|standardised \ deviance \ residual| ≤ 3$). Given the sizable correlation between frequency of Emoji use and age (see Data Description), we also confirmed that multicollinearity, i.e., model estimates being influenced by correlated predictors, was negligible by estimating generalised variance inflation factors for each predictor (all below the a priori criterion of 5; see Table \@ref(tab:q3-vif)). Finally,the Cook's distances, i.e., the average change in predictors if removing each observation, indicated three potentially influential observations (see Appendix, Figure \@ref(fig:q3-ass-diag)B). The threshold for this determination was 0.017, given by the equation $4/(N-k-1)$. After inspecting these observations (see Appendix, Table \@ref(tab:influ-obs-tab-q3)) and how they influenced model predictors (via DFBeta values; see Appendix, Table \@ref(tab:influ-tab-q3)), we performed two sensitivity analyses; (1) excluding one observation which seemed to influence the slope of age and frequency, and (2) excluding two observations influencing emoji category slopes and their interactions. Comparing these results to the model fitted to the full dataset we find no differences in significances or directions for the planned analyses (analysis of deviance: Table\@ref(tab:sens-ans-dev-q3); regression coefficients: \@ref(tab:sens-an-coef-tab-q3) and Figure \@ref(fig:sens-an-plot)). Therefore, we report the model for the full dataset below. For (1) we find no changes in the regression slopes, while for (2) we find minor shifts in the regression slopes for the thumbs up emoji, which we report briefly (see Sensitivity Analyses).

As shown in Table \@ref(tab:q3-dev-tab), likelihood ratio tests indicated that age significantly improved model fit above and beyond what frequency of emoji use alone could account for ($\chi^2$(`r ano_q3$Df[3]`) = `r round(ano_q3$Deviance[3],2)`, *p* `r print_p(ano_q3$p.value[3])`). The interaction between age and emoji category further significantly reduced deviance of the model ($\chi^2$(`r ano_q3$Df[5]`) = `r round(ano_q3$Deviance[5],2)`, *p* `r print_p(ano_q3$p.value[5])`) although inclusion of emoji category alone did not affect model deviance ($\chi^2$(`r ano_q3$Df[4]`) = `r round(ano_q3$Deviance[4],2)`, *p* `r print_p(ano_q3$p.value[4])`). Thus, age and its interaction with emoji category, each significantly contributed to improving predicted interpretation accuracy beyond what could be accounted for by frequency of emoji use.

```{r q3-dev-tab}
# proper row names
rownames(ano_q3)<- c(
  "Intercept-only", 
  "Emoji use frequency", 
  "Age",
  "Emoji category",
  "Age:Emoji category"
  )

# print table
ano_q3 |>
  mutate(Df = ifelse(is.na(Df) == T, "", Df),
         Deviance = ifelse(is.na(Deviance) == T, "", round(Deviance,2)),
         p.value = ifelse(is.na(p.value) == T, "", ifelse(p.value < 0.001, "< 0.001", round(p.value,3)))
         ) |>
  kable(digits = 2, 
        # proper column names
        col.names = c("Df", 
                      "Deviance", 
                      "Residual Df", 
                      "Residual Deviance", 
                      "p-value"),
        caption = "Emoji Interpretation: Analysis of Deviance Table",
        booktabs = T) |> 
  kable_styling(htmltable_class = "lightable-classic")
```

Looking at how these variables predicted accurate interpretation, we found that per year older, the odds of making an incorrect interpretation became `r round(1/exp(m1q3$coef[3]),2)` times bigger ($\frac {1}{OR}$; *OR* = `r round(exp(m1q3$coef[3]),2)`, 95 % *CI*[`r round(exp(confint(m1q3)[3,1]),2)`, `r round(exp(confint(m1q3)[3,2]),2)`]; *z* = `r round(coef(summary(m1q3))[,"z value"][3],2)`, *p* `r print_p(coef(summary(m1q3))[,"Pr(>|z|)"][3])`). However, this association with age was specific to the loudly crying face emoji (`r emoji::emoji("loudly crying face")`) and was moderated by which emoji was interpreted as suggested by the analysis of deviance. Specifically, the thumbs-up emoji (`r emoji::emoji("thumbs up")`) enhanced the negative effect of age on interpretation accuracy; for this emoji, the odds of making an incorrect interpretation for each year older was `r round(1/exp(m1q3$coef[7]),2)*round(1/exp(m1q3$coef[3]),2)` times bigger than for the loudly crying emoji (`r emoji::emoji("loudly crying face")`) ($\frac {1}{OR}$; *OR* = `r round(exp(m1q3$coef[7]),2)`, 95 % *CI*[`r round(exp(confint(m1q3)[7,1]),2)`, `r round(exp(confint(m1q3)[7,2]),2)`]; *z* = `r round(coef(summary(m1q3))[,"z value"][7],2)`, *p* `r print_p(coef(summary(m1q3))[,"Pr(>|z|)"][7])`). We also found that the odds of correctly interpreting the thumbs-up emoji (`r emoji::emoji("thumbs up")`) holding age constant were significantly lower than for the loudly crying face emoji  (`r emoji::emoji("loudly crying face")`) (*OR* = `r round(exp(m1q3$coef[5]),2)`, 95 % *CI*[`r round(exp(confint(m1q3)[5,1]),2)`, `r round(exp(confint(m1q3)[5,2]),2)`]; *z* = `r round(coef(summary(m1q3))[,"z value"][5],2)`, *p* `r print_p(coef(summary(m1q3))[,"Pr(>|z|)"][5])`). Meanwhile, the slightly smiling face emoji (`r emoji::emoji("slightly smiling face")`) did not differ significantly from the loudly crying face emoji (`r emoji::emoji("loudly crying face")`) for its odds of correct interpretation (*OR* = `r round(exp(m1q3$coef[4]),2)`, 95 % *CI*[`r round(exp(confint(m1q3)[4,1]),2)`, `r round(exp(confint(m1q3)[4,2]),2)`]; *z* = `r round(coef(summary(m1q3))[,"z value"][4],2)`, *p* `r print_p(coef(summary(m1q3))[,"Pr(>|z|)"][4])`) or how this changed with age (*OR* = `r round(exp(m1q3$coef[6]),2)`, 95 % *CI*[`r round(exp(confint(m1q3)[6,1]),2)`, `r round(exp(confint(m1q3)[6,2]),2)`]; *z* = `r round(coef(summary(m1q3))[,"z value"][6],2)`, *p* `r print_p(coef(summary(m1q3))[,"Pr(>|z|)"][6])`). We found no significant effect of emoji use frequency^[Note, that this discrepancy of significance for the frequency of emoji use between the analysis of deviance and logistic regression coefficient may be related to how much it uniquely reduces model deviance and its correlation with age. Specifically, it may share a large amount of the reduced deviance with age due to their correlation - thus, in the analysis of deviance due to its antecedency this overlap was attributed to it, yet, in the linear model only non-overlapping deviance is considered. This also suggests that age has a sizable unique impact on deviance compared to frequency.] or any other coefficients. A complete overview of the regression results as odds ratios are reported in Table \@ref(tab:q3-tab-model).

<div style='display: inline-block; max-width: 65%; vertical-align: top;float: inline-start; margin-inline-end: 10px'>
```{r q3-tab-model}
tab_model(m1q3, 
          transform = "exp",
          show.stat=T, 
          dv.labels = "Correct Emoji Interpretation", 
          pred.labels = c("Intercept", 
                          "Emoji use frequency", 
                          "Age", 
                          str_c("Emoji [", emoji::emoji("slightly smiling face"),"]"), 
                          str_c("Emoji [", emoji::emoji("thumbs up"),"]"), 
                          str_c("Age:Emoji [", emoji::emoji("slightly smiling face"),"]"), 
                          str_c("Age:Emoji [", emoji::emoji("thumbs up"),"]")), 
          string.stat = "z-statistic ", 
          string.p = "p-value ", 
          string.ci = "95 % CI", 
          string.est = "Odds Ratio ",
          show.r2 = F,
          show.dev = T,
          show.loglik = T,
          show.se = T,
          title = "(\\#tab:q3-tab-model) Interpretation Accuracy Model")
```
</div>

<div style='display: inline-block; max-width: 30%; vertical-align: top'>
```{r q3-model-plots, fig.cap="Predicted Probability of Correct Emoji Interpretation Age for Each Emoji Tested", fig.height=8}
q3_p2
```
</div>

Figure \@ref(fig:q3-model-plots) visualises the predicted probability of correctly interpreting emoji for the age by emoji category interaction; the probability of accurately interpreting the emoji for the sample age range, split by each emoji category, and holding frequency of emoji use constant (at 0). Emphasising the results of the regression coefficients, the probability of correctly interpreting the thumbs up emoji (`r emoji::emoji("thumbs up")`) seem to change more with age than the other emoji categories. Although as shown by the overlapping uncertainty ranges, the predicted effects may also be very similar for most ages.

## Sensitivity Analyses

We conducted two sensitivity analyses of these results due to potential influence. While the first sensitivity analysis demonstrated no change in the regression coefficients () or analysis of deviance (), we found two influential observations, which, from their DFBetas, indicated a strong influence on the emoji category coefficients and their interactions with age. Upon excluding these, the estimate of the thumbs-up emoji and its interaction became lower but more certain (); thus, the effect on interpretation accuracy of the thumbs-up emoji and how it interacts with age may be slightly smaller than the primary analysis suggests. We chose to retain these for the primary analysis since they did not affect the significance of any predictors, and their Cook's distances are relatively low (beneath the threshold of 0.017).

## Conclusion

We found that older age decreased how likely participants were to interpret emoji correctly. However, the extent of this was moderated by the emoji being interpreted. The thumbs-up emoji (`r emoji::emoji("thumbs up")`) had a generally lower likelihood of being interpreted correctly, which decreased more in older participants than the other emojis in the study. In short, age seems to have a negative impact on how emojis are interpreted, although the extent of this depends on the emoji.

# Appendix: Supplementary Tables and Figures

## Data Preparation

```{r ini-pairs-panels, fig.cap="Marginal Distributions and Between-Variable Relationships for Pre-Processed Data", fig.width=11,fig.height=13}
emoji |> 
  select("age", "EVS", "freq_emu", "em_cat", "EI", "opsys") |>
  mutate(em_cat = factor(em_cat, labels = c("Cry", "Smile", "Thumbs", "Upside-down"))) |>
  ggpairs(columnLabels = c("Age", "Emotional Valence Score", "Frequency of Emoji Use", 
                           "Emoji Category", "Emoji Interpretation", "Operating System")
    ) 
```

```{r exclude} 
excl_tab |>
  mutate(opsys = factor(opsys, labels = c("Android", "Apple"))) |>
  kable(col.names = c("Name", "Age", "Operating system", "Emoji use frequency",
                      "Emoji category", "Emotional valence score",
                      "Emoji Interpretation", "Reason for exlcusion"),
        caption = "Excluded Observations",
        booktabs = T, digits = 2) |> 
  kable_styling(htmltable_class = "lightable-classic")
```

## Data Description

```{r qq-plot-freq, fig.cap="QQPlots of Frequency of Emoji for (A) Apple and (B) Android Users", fig.height=4}
emoji_qq1 <- emoji_clean|>
  filter(opsys=="Apple")
emoji_qq2 <- emoji_clean|>
  filter(opsys=="Android")

par(mfrow = c(1, 2)) #combining plots in one line 

qqnorm(
       main = "A) Normal Q-Q Plot: Apple",
       emoji_qq1$freq_emu)
qqline(emoji_qq1$freq_emu)

qqnorm(
  main = "B) Normal Q-Q Plot: Android",
  emoji_qq2$freq_emu)
qqline(emoji_qq2$freq_emu)
```

## The Emotional Effect of Emojis

```{r cat-code-tab}
kable(contrasts(emoji_clean$em_cat), col.names = c("D1", "D2"), 
      caption = "Emoji Category Treatment Contrast Coding Scheme",
      booktabs = T) |>
  kable_styling(htmltable_class = "lightable-classic", full_width = T)
```

```{r q2-vif}
vif_q2 <- vif(m2intq2)[,1:2]

rownames(vif_q2) <-c("Emoji use frequency","Age","Emoji category","Age:Emoji category")

kable(vif_q2, digits = 2, caption = "Variance Inflation Factors for Predictors of Emotional Effect") |>
  kable_styling(htmltable_class = "lightable-classic")
```

```{r q2-influence}
inf_mat_q2<- influence.measures(m2intq2)$infmat
inf_mat_q2[c(2, 13, 175),] |> 
  kable(digits = 2,
        col.names = c("DFBeta intercept", "DFBeta frequency", "DFBeta age", str_c("DFBeta Emoji [", emoji::emoji("slightly smiling face"),"]"), str_c("DFBeta Emoji [", emoji::emoji("thumbs up"),"]"), str_c("DFBeta age:Emoji [", emoji::emoji("slightly smiling face"),"]"), str_c("DFBeta age:Emoji [", emoji::emoji("thumbs up"),"]"), "DFFit", "Covariance ratio", "Cook's Distance", "Hat values"),
        caption = "Influence Measures for Potentially Influential Values",
        booktabs = T) |>
  kable_styling(htmltable_class = "lightable-classic")
```

```{r ass-for-q2, fig.cap="Assumptions for Linear Regression Model"}
par(mfrow = c(2, 2))

plot(m2intq2, which = 1, main = "A")
plot(m2intq2, which = 2, main = "B")
plot(m2intq2, which = 3, main = "C")
plot(m2intq2, which = 4, main = "D")
```

## Accuracy of Emoji Interpretation

```{r q3-ass-diag, fig.cap= "(A) Standardised Deviance Residuals and (B) Cook's Distances for the Interpretation Accuracy Model", fig.height=4, fig.width=10}
par(mfrow = c(1, 2))
plot(rstandard(m1q3, type = 'deviance'), ylab = 'Standardised Deviance Residuals',
     main = "(A) Standardised Deviance Residuals")
plot(m1q3, which=4, main = "(B) Cook's Distances" )
```

```{r q3-vif}
vif_q3 <- vif(m1q3)[,1:2]

rownames(vif_q3) <-c("Emoji use frequency","Age","Emoji category","Age:Emoji category")

kable(vif_q3, digits = 2,
      caption = "Variance Inflation Factors for Predictors of Interpretation Accuracy", booktabs = T) |>
  kable_styling(htmltable_class = "lightable-classic")
```

```{r influ-tab-q3}
infl_q3 <-influence.measures(m1q3)$infmat 

infl_q3[c(13, 75, 218),] |> 
  kable(digits = 2,
        col.names = c("DFBeta intercept", "DFBeta frequency", "DFBeta age", str_c("DFBeta Emoji [", emoji::emoji("slightly smiling face"),"]"), str_c("DFBeta Emoji [", emoji::emoji("thumbs up"),"]"), str_c("DFBeta age:Emoji [", emoji::emoji("slightly smiling face"),"]"), str_c("DFBeta age:Emoji [", emoji::emoji("thumbs up"),"]"), "DFFit", "Covariance ratio", "Cook's Distance", "Hat values"),
        caption = "Influence Measures for Potentially Influential Values",
        booktabs = T) |>
  kable_styling(htmltable_class = "lightable-classic")
```

```{r influ-obs-tab-q3}
emoji_q3_analysis[c(13, 75, 218),-c(8:10)] |> kable(digits = 2,
        col.names = c("Name", "Age", "Operating system", "Emoji use frequency",
                      "Emoji category", "Emotional valence score",
                      "Emoji Interpretation", "Reason for exlcusion"),
        caption = "Potentially Influential Observations",
        booktabs = T) |>
  kable_styling(htmltable_class = "lightable-classic")
```

```{r sensitivity analysis}
m2q3 <- glm(EI_bi ~ freq_emu + age_mc*em_cat, data = emoji_q3_analysis[-c(75,218),], family = binomial)
m3q3 <- glm(EI_bi ~ freq_emu + age_mc*em_cat, data = emoji_q3_analysis[-c(13),], family = binomial)
```

```{r sens-ans-dev-q3}
ano2_q3 <- anova(m2q3, test = "Chisq")
ano3_q3 <- anova(m3q3, test = "Chisq")

ano_row <- c(
  "Intercept-only", 
  "Frequency", 
  "Age",
  "Emoji",
  "Age:Emoji")
rownames(ano2_q3) <- ano_row
rownames(ano3_q3) <- ano_row

ano2_q3 |>
    rename("p.value" = "Pr(>Chi)") |>
  mutate(Df = ifelse(is.na(Df) == T, "", Df),
         Deviance = ifelse(is.na(Deviance) == T, "", round(Deviance,2)),
         p.value = ifelse(is.na(p.value) == T, "", ifelse(p.value < 0.001, "< 0.001", round(p.value,3)))) |>
  kable(digits = 2, 
        # proper column names
        col.names = c("Df", 
                      "Deviance", 
                      "Res. Df", 
                      "Res. Deviance", 
                      "p-value"),
        caption = "Emoji Interpretation: Analysis of Deviance Table (Sensitivity Analysis 1)",
        booktabs = T) |> 
  kable_styling(htmltable_class = "lightable-classic", position = "float_left", full_width = F)

ano3_q3 |>
  rename("p.value" = "Pr(>Chi)") |>
  mutate(Df = ifelse(is.na(Df) == T, "", Df),
         Deviance = ifelse(is.na(Deviance) == T, "", round(Deviance,2)),
         p.value = ifelse(is.na(p.value) == T, "", ifelse(p.value < 0.001, "< 0.001", round(p.value,3)))) |>
  kable(digits = 2, 
        # proper column names
        col.names = c("Df", 
                      "Deviance", 
                      "Res. Df", 
                      "Res. Deviance", 
                      "p-value"),
        caption = "Emoji Interpretation: Analysis of Deviance Table (Sensitivity Analysis 2)",
        booktabs = T) |> 
  kable_styling(htmltable_class = "lightable-classic", position = "float_right", full_width = F)
```

```{r sens-an-coef-tab-q3}
tab_model(m1q3, m2q3, m3q3,show.stat=T, 
          dv.labels = c("Reported model", "Sensitivity Analysis 1", "Sensitivity Analysis 2"), 
          pred.labels = c("Intercept", 
                          "Emoji use frequency", 
                          "Age", 
                          str_c("Emoji [", emoji::emoji("slightly smiling face"),"]"), 
                          str_c("Emoji [", emoji::emoji("thumbs up"),"]"), 
                          str_c("Age:Emoji [", emoji::emoji("slightly smiling face"),"]"), 
                          str_c("Age:Emoji [", emoji::emoji("thumbs up"),"]")), 
          string.stat = "z-statistic ", 
          string.p = "p-value ", 
          string.ci = "95 % CI", 
          string.est = "Odds Ratio ",
          show.r2 = F,
          show.dev = T,
          show.loglik = T,
          show.se = T,
          title = "(\\#tab:sens-an-coef-tab-q3) Table of Coefficients for the Reported Model and Sensitivity Analyses for Emoji Interpretation Accuracy")
```

```{r sens-an-plot, fig.width=9, fig.cap="Predicted Probability of Correct Emoji Interpretation Age for Each Emoji Tested for (A) Sensitivity Analysis 1 and (B) Sensitivity Analysis 2", fig.width= 8, fig.height=3, fig.align='center'}
# Age and emoji category plot
(broom::augment(m2q3, newdata = q3_plotdata_age_em, 
               type.predict = "link",
               se_fit=TRUE) |>
  mutate(
    .lower = l2p(.fitted - 1.96*.se.fit),
    .upper = l2p(.fitted + 1.96*.se.fit),
    .fitted = l2p(.fitted),
    age = I(age_mc + mean(emoji_clean$age))
  ) |> 
  ggplot(aes(x=age,y=.fitted, group = em_cat, ymin=.lower,
             ymax=.upper))+
  geom_line(aes(color = em_cat))+
  geom_ribbon(alpha=.2, aes(fill = em_cat))+
  scale_colour_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  labs(x = "Age", y = "Probability of Correct Emoji Interpretation", 
       color =  "Emoji Category", fill ="Emoji Category", title = "(A) Sensitivity Analysis 1")+
  theme_light())|
# Age and emoji category plot
(broom::augment(m3q3, newdata = q3_plotdata_age_em, 
               type.predict = "link",
               se_fit=TRUE) |>
  mutate(
    .lower = l2p(.fitted - 1.96*.se.fit),
    .upper = l2p(.fitted + 1.96*.se.fit),
    .fitted = l2p(.fitted),
    age = I(age_mc + mean(emoji_clean$age))
  ) |> 
  ggplot(aes(x=age,y=.fitted, group = em_cat, ymin=.lower,
             ymax=.upper))+
  geom_line(aes(color = em_cat))+
  geom_ribbon(alpha=.2, aes(fill = em_cat))+
  scale_colour_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  labs(x = "Age", y = "P(Correct Emoji Interpretation)", 
       color =  "Emoji Category", fill ="Emoji Category", title = "(B) Sensitivity Analysis 2")+
  theme_light())
```
