---
title: "Aggregating Anteaters Project"
output: 
  html_document:
    number_sections: true
date: "2023-11-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE, # (JMEP) makes sure html doc doesn't print warnings
                      message = FALSE) # (JMEP) makes sure html doc doesn't print messages
```
```{r}
library(tidyverse)
library(GGally) # (JMEP lib to make pretty pairs panel)

source("https://edin.ac/4616rYu")
get_my_data(group_name = "aggregating_anteaters")

# (JMEP) cleaning data of weird values - see notes 
emoji_clean <- emoji |>
  filter(is.na(age) == F,
         age > 2,
         opsys != "windows",
         freq_emu >= 0) |>
  mutate(opsys = ifelse(opsys == "appple", "apple", opsys),
         opsys = as.factor(opsys))
```


# Data Description

```{r}
# (JMEP) pretty paris panel
emoji_clean |> 
  select(age, freq_emu, EVS) |> 
  ggpairs()
```

# The Emotional Effect of Emojis

# Accuracy of Emoji Interpretation

# Appendix A: Supplementary Tables and Figures

# Notes for report (to be deleted)

found this cool way of generating lm equation :0 https://bookdown.org/yihui/rmarkdown-cookbook/equatiomatic.html

(JMEP; 16/11/2023 - midnight zoomies) found this cool way of generating lm equation :0 https://bookdown.org/yihui/rmarkdown-cookbook/equatiomatic.html

(JMEP; 16/11/2023 - midnight zoomies) Would be helpful if we could do all our code for each section in one chunk. Then we can call tables/figures where we need them and refer to numbers in inline code. Inline code example: `r mean(emoji$age)` (there is an NA in age, booo)

(JMEP; 16/11/2023 - midnight zoomies) I looked into age. There is one NA, one person who is -100 years old and one that is 1 year old. I think we can reliably remove them (done in emoji_clean). There are also a bunch (`r nrow(filter(emoji, is.na(age) == F & age < 18 & age > 1))` to be exact) that are under 18 (between `r range(filter(emoji, is.na(age) == F & age < 18 & age > 1)$age)[1]` and `r range(filter(emoji, is.na(age) == F & age < 18 & age > 1)$age)[2]`), whom I am not sure if we should remove??
I also noticed some other unusual stuff. Frequency ratings below 0, and a typo in "Apple" for one of the operating systems ("Appple"). There are also only two windows users which isn't really helpful in terms of analysis - might wanna exclude them.